COG-ED Manuscript

### 2022-06-13 06_Paper/COG-ED/Manuscript.Rmd
removed paired contrast of H1a

```{r, echo=FALSE, message=FALSE, warning=FALSE}
apa_table(
  hypothesis1a_contrasts,
  caption = "Paired contrasts for the rmANOVA comparing $d'$ between n-back levels",
  note = "The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
  escape = FALSE,
  placement = "H"
)
```

@@

`r apa_print(hypothesis3b_model)$full_result$nfcmedian`, §BF10=$ `r format(extractBF(hypothesis3b_BF["nfcmedian"])$bf, digits = 2)`

@@

`r apa_print(hypothesis3b_model)$full_result$level`, §BF10=$ `r format(extractBF(hypothesis3b_BF["level"])$bf, digits = 2)`

@@

`r apa_print(hypothesis3b_model)$full_result$nfcmedian_level`, §BF10=$ `r format(extractBF(hypothesis3b_BF["level + nfcmedian"])$bf, digits = 2)`

>>>>

@@

`r apa_print(hypothesis3b_model)$full_result$nfcmedian`, $BF10=$ `r format(extractBF(hypothesis3b_BF["nfcmedian"])$bf, digits = 2)`

@@

`r apa_print(hypothesis3b_model)$full_result$level`, $BF10=$ `r format(extractBF(hypothesis3b_BF["level"])$bf, digits = 2)`

@@

`r apa_print(hypothesis3b_model)$full_result$nfcmedian_level`, $BF10=$ `r format(extractBF(hypothesis3b_BF["level + nfcmedian"])$bf, digits = 2)`
